---
title: "FPS_Calculations"
author: "Evan Arias-Johnon"
date: "2024-03-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Function 1: TTK_Calc

The calculation wants to know how fast a weapon in game could optimally take down an opponent. The arguemets are as followed:

RPM - Rounds per Minute 
Shots to Eliminate Opponent - Bullets Required 

How the formula looks: `(60/RPM)*(Shots_Required - 1)`
```{r cars}

TTK_Calc <- function(RPM,Shots_Required){
  #Rounding to produce the first 2 decimal places
  Time_to_kill <- round((60/RPM)*(Shots_Required - 1),2)
  return(Time_to_kill)
}

#Rounds Per Minute
RPM <- 140

#Shots Required to Kill
Shots_Required <- 3

#using the Function 
TTK_Calc(X,Y)


```
Function 2: Bullets_to_Eliminate 

So technically, you could use this function first to determine shots_to_elimante in the function listed before. The arguments are as followed:

- Total_Health -> Total Player Health (In the game I )
- DPB -> Damage per Bullet


Eventually I would like to help determine how many Headshots to body shots is required, but this is a start. 



```{r pressure, echo=FALSE}
Bullets_to_Elimination <- function(Total_Health,DPB){
  #Rounding to produce the first decimal place
  BtE <- round((Total_Health/DPB),1)
    #If the Mod of BtE is not equal to ZERO
     if ((BtE %% 1) != 0) {
       #Then take the mod of BtE and subtract 1 from it
        BtE_Remainder <- 1 - (BtE %% 1)
        #Then take BtE and add the remainder to it so you get to the nearest whole number
        BtE <- BtE + BtE_Remainder
     } else {
       #If it prints a clean value, just print BtE
       BtE <- BtE
     }
  return(BtE)
}

#Total Health
Total_Health <- 230

#Damage per Bullet
DPB <- 61

#Calling the function
Bullets_to_Elimination(Total_Health,DPB)


```
The last set of formulas I want to use is  `standardization/Z-score` and `normalization`.
These all play nicely together, however I normally use standarization. This allows me to view multiple values within the same category on a variety of scales. In this case I have 3 cateogries I break things into which are `close-range`, `mid-range`, `long-range`.

However this package will not go that deep. 

Standardization =
- Value of Choice from Column X
- Mean of Values of Column X
- Standard Deviation of Column X

FORMULA: `(Value - Mean)/(Standard Deviation)`

Normalization = 
- Value of choice from Column X 
- Min Value of Column X
- Max valaue of Column X

FORMULA: `(Value - Min)/(Max-Min)`



```{r}
standardization <- function(Value,Mean, SD){
  #Rounding to produce the first 2 decimal places
  Standard_Value <- round((Value - Mean)/(SD),2)
  return(Standard_Value)
}

Value <- 16
Mean <- 46
SD <- 26

standardization(Value,Mean,SD)


Normalization <- function(Value,Min, Max){
  #Rounding to produce the first 2 decimal places
  Normal_Value <- round((Value - Min)/(Max-Min),2)
  return(Normal_Value)
}

Value <- 46
Min <- 16
Max <- 86

Normalization(Value,Min,Max)



```




Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
